### 2020-05-09 ArticleAcortado.tex
Acrotar más

\newtheorem{proposition}{Proposition}[section]
\newtheorem{fact}{Fact}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{obs}{Observation}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{propdef}{Proposition / Definition}[section]
\newtheorem{remark}{Remark}[section]

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\sim_#1}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\ehr}{\textsc{Ehr}}
\newcommand{\PR}[1]{\mathrm{Pr}\big(#1\big)}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\InR}[1]{\left\{ #1_R \right\}_{R\in \sigma}}
\newcommand{\sep}{\noindent\rule{2cm}{0.4pt}}
\newcommand{\aut}{\mathrm{aut}}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\begin{document}
\begin{abstract}
	We consider a finite relational vocabulary $\sigma$
	and a first order theory $T$ for $\sigma$ 
    composed of symmetry and 
    anti-reflexivity axioms. We define a binomial random model of finite 
    $\sigma$-structures that satisfy $T$ and show that first order properties have 
    well defined asymptotic probabilities in the sparse 
    case. It is also shown that those limit probabilities are well-behaved with
    respect to some parameters that represent edge densities. 
    An application of these results to the problem of random Boolean 
    satisfiability is presented afterwards. 
    We show that there is no first order property of $k$-CNF formulas
    that implies unsatisfiability and holds for almost all typical 
    unsatisfiable formulas when the number of clauses is linear.

@@

The short proof of this theorem is as follows: 
It is a known fact that there are positive constants
$c_0\leq c_1$ such that $G(n, c/n)$ is a.a.s $3$-colorable
if $c<c_0$ and it is a.a.s non $3$-colorable if $c>c_1$ 
REFERENCES NEEDED.
Suppose that $P$ is a FO graph property that implies
non-$3$-colorability. Then, because of this implication,
for all values of $c$
\[\Ln \mathrm{Pr}\big( G(n, c/n) 
\text{ satisfies } P \big) \leq \Ln \mathrm{Pr}\big( G(n, c/n) 
\text{ is not }	3\text{-colorable}\big).\]
In consequence the asymptotic probability that $G(n,c/n)$ 
satisfies $P$ is zero when $c<c_0$. By Lynch's theorem, if 
$P$ is definable in FO logic then this asymptotic probability
varies analytically with $c$. Using the fact that any analytic 
function that takes value zero in a non-empty interval must 
equal zero everywhere, we obtain that $G(n,c/n)$ a.a.s does 
not satisfy $P$ for any value of $c$. 
As a consequence the theorem follows.  \par

@@

Given a positive natural number $n$, we will write
$[n]$ to denote the set ${1,2,\dots,n}$.\par
Given a set $S$ and a natural number $k\in \N$
we will use $\binom{S}{k}$ to denote the set of 
subsets of $S$ whose size is $k$. \par
Given numbers, $n,m\in \N$ with $m\leq n$ we denote by
$(n)_m$ the $m$-th falling factorial of $n$. \par
Given a set
$S$ and a number $n\in \N$ with $n\leq |S|$ we define
$(S)_n$ as the subset of $S^n$ consisting of the $n$-tuples
whose coordinates are all different. 
We also define $S^*:=\bigcup_{n=0}^\infty S^n$ and
$(S)_*:=\bigcup_{n\leq |S|} (S)_n$. 
Given two tuples $\overline{x},\overline{y}\in S^*$
we write $\overline{x}^\smallfrown \overline{y}$ to denote their 
concatenation. Given a tuple 
$\overline{x}\in S^*$ and an element $x\in S$ the expression
$x\in \overline{x}$ will mean that $x$ appears as some coordinate
in $\overline{x}$. We will at times make an abuse of notation and
treat the tuple $\overline{x}$
as the set of elements $x\in \overline{x}$. 
We will use the convention that over-lined variables
, like $\overline{x}$, denote ordered tuples of arbitrary length.
Given an ordered tuple $\overline{x}$
we define the number $len(\overline{x})$ as its length. 
Given a map $f:X\rightarrow Y$ between two sets $X, Y$ and 
an ordered tuple $\overline{x}:=(x_1,\dots,x_a)\in X^*$ 
we define $f(\overline{x})\in Y^*$ as the tuple 
$(f(x_1),\dots,f(x_a))$.
\par

Let $S$ be a set, $a$ a positive natural number, 
and $\Phi$ a group of permutations over 
$[a]$. Then $\Phi$ acts naturally over
$S^a$ in the following way: Given $g\in \Phi$ and
$\overline{x}:=(x_1,\dots,x_a)\in S^a$ we define 
$g\cdot \overline{x}$ 
as the tuple $(x_{g(1)},\dots,x_{g(a)})$. 
We will denote by $S^a/\Phi$ to the quotient
of the set $S^a$ by this action. Given an element
$\overline{x}:=(x_1,\dots, x_a)\in S^a$ we will denote its equivalence
class in $S^a/\Phi$ by $[x_1,\dots,x_a]$ or $[\overline{x}]$.
Thus, for any
$g\in \Phi$, by definition $[x_1,\dots,x_a]=[x_{g(1)}
,\dots,x_{g(a)}]$. The notations $\overline{x}$ and
$(x_1,\dots, x_a)$ 
will be reserved 
to ordered tuples while 
$[\overline{x}]$ and
$[x_1,\dots,x_a]$ will denote ordered tuples modulo the
action of some arbitrary group of permutations. Which group is
this will depend on the ambient set where $[x_1,\dots,x_a]$ belongs
and it should either be clear from context or not be relevant.\par

@@

We can think any structure $G$ in $\mathcal{C}$
as a ``multi-hypergraph" whose vertices are the elements
of the universe of $G$. Each relation $R\in \sigma$, can be 
represented over $G$ as an ``edge set" formed by tuples vertices
of size $ar(R)$ modulo the permutations in $\Phi_R$. Furthermore, 
repetitions of vertices in the positions given by
$P_R$ are not allowed in these tuples.\par
The following definitions make this ideas formal. Notice that they 
depend on our fixed choice of $\sigma$, $\{\phi_R\}_{R\in \sigma}$
and $\{P_R\}_{R\in \sigma}$.

\begin{definition} 
	Let $V$ be a set, and let $R\in \sigma$.
	We define the \textbf{total edge set over $V$
	given by $R$} as
	\[ E_R[V]= (V^{ar(R)}/\Phi_R) \quad \setminus 
	\quad X, \]
	where
	\[
	X=
	\Big\{ [x_1,\dots,x_{ar(R)}]  
	\quad \Big| \quad
	x_1,\dots,x_{ar(R)}\in V, \,
	\text{ and } 
	 \, x_i=x_j \text{ for some } 
	\{i,j\}\in P_R \Big\}.
	\]
	Also, we will say that the \textbf{sort} of the elements $e\in E_R[V]$
	is $R$. 
\end{definition}

That is, $E_R[V]$ contains all the ``$ar(R)$-tuples of elements
in $V$ modulo the permutations
in $\phi_R$" 
excluding those that contain some repetition of elements in
the positions given by $P_R$.\par
The fact that the elements $e\in E_R(V)$ are of sort $R$ 
is a technical detail
introduced so that for any different relation symbols $R_1$ and
$R_2$ it holds $E_{R_1}(V)\cap E_{R_2}(V)=\emptyset$ even in the case
that $ar(R_1)=ar(R_2)$, $\Phi_{R_1}=\Phi_{R_2}$ and $P_{R_1}=P_{R_2}$.\par

In the case where $V=[n]$ we will write simply $E_R[n]$ instead
of $E_R[[n]]$.

\begin{definition} 
We call $\mathcal{C}$-\textbf{hypergraph}, or simply hypergraph, 
to a pair $G=\Big(V(G),\{E_R(G)\}_{R\in\sigma}\Big)$,
where for each $R$, $E_R(G) \subseteq E_R[V]$.
\end{definition}

Hypergraphs, as we have defined them, 
can be naturally interpreted as
structures from $\mathcal{C}$ 
in the following way: 
given an hypergraph $G:=(V,\{E_R\}_{R\in \sigma})$,
we can construct a $\sigma$-structure $\mathcal{G}$ whose universe is
$V$, and for any $R\in \sigma$ we define
$R^\mathcal{G}\subseteq V^{ar(R)}$ as the set of tuples
$\overline{x}\in V^{ar(R)}$ such that
$[\overline{x}]\in E_R$. Clearly $\mathcal{G}$
satisfies by definition the 
symmetry and anti-reflexivity
axioms given at the beginning of this section. It is easy to
see that this process induces
a one-to-one identification between 
structures in $\mathcal{C}$ and hypergraphs. \par

\subsection{Hypergraph notation and nomenclature}

We will use standard nomenclature and notation
from graph theory with some additions. Given an 
hypergraph $G$ we will call its \textbf{vertex set} to $V(G)$ 
and \textbf{vertices} 
to the elements $v\in V(G)$. Likewise, each of 
the $E_R(G)$'s will be called an \textbf{edge set} and its elements, 
\textbf{edges}. Given an edge, $e\in V(G)$ we will denote by $V(e)$
the set of all vertices that participate in $e$.

\par
Given an hypergraph $G$ we define the set $E(G)$ as the
union $\cup_{R\in \sigma}E_R(G)$. Notice that this union 
is disjoint because elements from different $E_R(G)$'s 
are of different sorts. Thus, $|E(G)|=\sum_{R\in \sigma} 
|E_R(G)|$. Analogously, given a set $V$, we define
$E[V]:=\cup_{R\in \sigma} E_R[V]$.
Given an edge $e\in E[V]$ we define $R(e)$
as the sort of $e$, i.e.,
the unique relation symbol $R(e)\in \sigma$
such that $e\in E_{R(e)}[V]$.

@@

We define the \textbf{excess} $ex(G)$ of an hypergraph $G$ as the number
\[
ex(G):= \big(\sum_{R\in \sigma} (ar(R)-1)|E_R(G)|\big) - |V(G)|.  
\] 
That is, the excess of $G$ is its "weighted number of edges"
minus its number of vertices. \par
An hypergraph $G$ is \textbf{connected} if for any two vertices $v,u\in V(G)$
there is a sequence of edges $e_1,\dots, e_m\in E(G)$ such that
$v\in V(e_1), u\in V(e_m)$ and for each $i\in [m-1]$, 
$V(e_i)\cap V(e_{i+1})\neq \emptyset$. It holds that
$ex(G)\geq -1$ for any connected hypergraph.
\par Given a connected hypergraph $G$ 
and vertices $v,u\in V(G)$, we say that $G$ is
a \textbf{path} between $v$ and $u$
if $G$ 
does not contain any connected proper sub-hypergraph containing both $v,u$.
\par
A connected hypergraph $G$ is a \textbf{tree} if $ex(G)=-1$. 
\par A connected hypergraph $G$ is called \textbf{dense} if $ex(G)>0$.\par
A connected hypergraph $G$ with $ex(G)\geq 0$ is called \textbf{saturated} 
if for any non-empty proper sub-hypergraph
$H\subset G$ it holds $ex(H)<ex(G)$.
% It is satisfied that any connected hypergraph $G$
%with $ex(G)\geq 0$ contains a unique saturated sub-hypergraph $H$ with $ex(H)=ex(G)$.
\par
A connected hypergraph $G$ with $ex(G)=0$ is called \textbf{unicycle}. 
A saturated unicycle is called a \textbf{cycle}. \par
Given an hypergraph $G$ we define the following metric, $d$, over $V(G)$:
\[ d^G(u,v)= \min_{\substack{H \subset G\\ 
		H \text{ connected }\\
		u,v\in V(H)}} |E(H)| .\]
That is, the distance between $v$ and $u$ is the minimum number of
edges necessary to connect $v$ and $u$. 
If such number does not exist we define $d^G(u,v)=\infty$. \par
As usual, define $d^{G}(X,Y)$ for sets $X,Y\subset V(G)$ as the minimum
distance $d(u,v)$ where $u\in X$ and $v\in Y$. 
When $X=\{x\}$ we will omit the brackets and write
$d^G(x,Y)$ instead of $d^G(\{x\},Y)$, for example.
When $G$ 
is understood or not relevant we will usually simply denote the 
distance by $d$ instead of $d^G$. \par

Given set of vertices vertex, $X\subseteq V(G)$, 
we denote by $N^G(X;r)$ the $r$-\textbf{neighborhood} of $X$ in 
$G$. That is,  $N^G(X;r)= G[Y]$, where $Y\subseteq V(G)$ is 
the set:
\[ Y:= \{ u \in V(G) \ | \ d(X,u)\leq r   \}. \]
In particular, when $X$ is a singleton $\{v\}$, we
will write $N^G(v;r)$ instead of $N^G(\{v\};r)$.
As before, we will usually drop the ``$G$'' from our 
notation when $G$ is understood or not relevant.  \par

We will often write tuples of vertices instead of sets
inside of $d(\cdot\, , \cdot)$ and $N(\cdot\, ;r)$. In those cases
we are treating those tuples as sets as specified in
\cref{subsect:notation}.

\subsection{Copies of Hypergraphs}

Given two hypergraphs $H_1, H_2$ an \textbf{isomorphism} 
$f$ between them is a bijection $f: V(H_1)\rightarrow V(H_2)$
such that for any $R\in \sigma$, a tuple $\overline{v}\in V(H_1)^*$
forms an edge $[\overline{v}]\in E_R(H_1)$ if and only
if $[f(\overline{v})]\in E_R(H_2)$. We say that $H_1$ and
$H_2$ are isomorphic, written as $H_1\simeq H_2$, if there exists
some isomorphism between them.\par

Let $H$ be an hypergraph. An \textbf{automorphism} of $H$
is an isomorphism from $H$ to itself. We will denote by
$\aut(H)$ the number of such automorphisms. \par

Let, $\mathbb{H}$ be an isomorphism class of hypergraphs. Let
$H\in \mathbb{H}$ be a representative of the class. 
Then we define $ex(\mathbb{H})$ as $ex(H)$. Clearly this definition
does not depend on the choice of $H$. The expressions
$\aut(\mathbb{H})$,
$|V(\mathbb{H})|$, $|E(\mathbb{H})|$ or
$|E_R(\mathbb{H})|$ for $R\in \sigma$ are defined 
in an analogous way.\par

Let $H$ be an hypergraph and let $V$ be a set. We define the
set $Copies(H,V)$ as the set of hypergraphs $H^\prime$ such that
$V(H^\prime)\subset V$ and $H\simeq H^\prime$. Analogously, if
$\mathbb{H}$ is an isomorphism class of hypergraphs we define
$Copies(\mathbb{H},V)$ as the set of hypergraphs $H^\prime$ 
that satisfy
$V(H^\prime)\subset V$ as well as $H^\prime \in \mathbb{H}$.   \par

In our proofs it will be useful to consider colorings over 
hypergraphs as a way to assign extra information to their 
vertices.

\begin{definition} \label{def:color}
	Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
	is a pair $(H, \chi)$ where $H$ is an hypergraph
	and $\chi: V(H)\rightarrow \Sigma$ is a map 
	called \textbf{$\Sigma$-coloring} of $H$.
\end{definition}

	Given two $\Sigma$-hypergraphs $(H_1,\chi_1)$
	and $(H_2,\chi_2)$, an \textbf{isomorphism} between them is
	a bijection $f:V(H_1)\rightarrow V(H_2)$ satisfying
	that $f$ is an hypergraph isomorphism between $H_1$ and
	$H_2$ as well as $\chi_2(f(v))=\chi_1(v)$ for all $v\in V(H_1)$.
	We say that $(H_1,\chi_1)$ is isomorphic to $(H_2,\chi_2)$,
	written as $(H_1, \chi_1)\simeq (H_2,\chi_2)$, if there exists an
	isomorphism between them.
	\par	 
	Let $(H,\chi)$ be a $\Sigma$-hypergraph, an 
	\textbf{automorphism} of $(H,\chi)$ is an 
	isomorphism from it into itself. We will denote
	by $\aut(H,\chi)$ the number of such automorphisms. 
	\par
	As with the case of hypergraphs, if $\mathbb{H}$ is 
	an isomorphism class of $\Sigma$-hypergraphs
	then the expressions $\aut(\mathbb{H})$ and
	$|V(\mathbb{H})|$ are defined via representatives. \par
	Let $(H,\chi)$ be a $\Sigma$-hypergraph and let $V$ be a set.
	We define the set $Copies\big(
	(H,\chi),\, \, V\big)$ as the set of $\Sigma$-hypergraphs
	$(H^\prime,\chi^\prime)$ satisfying $V(H^\prime)\subset V$ and
	$(H,\chi)\simeq (H^\prime,\chi^\prime)$. Let $\mathbb{H}$ be 
	an isomorphism class of $\Sigma$-hypergraphs. Then the set
	$Copies(\mathbb{H}, V)$ is defined as the set of $\Sigma$-hypergraphs
	$(H^\prime,\chi^\prime)$ such that 
	$V(H^\prime)\subset V$ and
	$(H^\prime,\chi^\prime)\in \mathbb{H}$. 
	Let $v\in V$ and $s\in \Sigma$. We define the
	set $Copies\big(\mathbb{H}, V;\,\, (v,s)\big)$ 
	as the set of $\Sigma$-hypergraphs
	$(H^\prime,\chi^\prime)\in Copies(\mathbb{H}, V)$
	that satisfy $v\in V(H^\prime)$ as well as
	$\chi^\prime(v)=s$.

@@

%Let $G_n$ denote a random hypergraph in 
%$G^\mathcal{C}(n,\overline{p})$, where 
%$\bar{p}:=p_1,\dots,p_t$, and 
%we allow each $p_i$ to depend on $n$. 
As in the case of Lynch's theorem, we are interested in the
"sparse regime" of $G^\mathcal{C}(n,\overline{p})$, were the 
expected number of edges each sort is linear. 
%In other words, we want that
%$\mathrm{E}[m_i(G_n)]=\Theta(n)$ for all $i$'s.
This is achieved when each of the $p_R$'s are 
of the form $\beta_R/n^{ar(R)-1}$ for some 
positive real numbers $\InR{\beta}$.
From now on we will write $G_n\left(\InR{\beta}\right)$
to denote a random sample of 
$G^\mathcal{C}\left(n,\left\{ \frac{
\beta_R}{n^{ar(R)-1}}\right\}_{R\in\sigma}\right)$.
When the choice of $\InR{\beta}$ is not relevant
we will write $G_n$ instead of 
$G_n\left(\InR{\beta}\right)$.\par

@@

A more complete introduction to the subject can be found in
\cite[Section 2]{finitemodeltheory1}, for example.\par

>>>>

\theoremstyle{definition}
\newtheorem{proposition}{Proposition}[section]
\newtheorem{fact}{Fact}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{obs}{Observation}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{propdef}{Proposition / Definition}[section]
\newtheorem{remark}{Remark}[section]

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\sim_#1}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\ehr}{\textsc{Ehr}}
\newcommand{\PR}[1]{\mathrm{Pr}\big(#1\big)}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\InR}[1]{\left\{ #1_R \right\}_{R\in \sigma}}
\newcommand{\sep}{\noindent\rule{2cm}{0.4pt}}
\newcommand{\aut}{\mathrm{aut}}

\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\begin{document}
\begin{abstract}
	We extend the convergence law for sparse random graphs proven
	by Lynch to arbitrary relational languages.
	We consider a finite relational vocabulary $\sigma$
	and a first order theory $T$ for $\sigma$ 
    composed of symmetry and 
    anti-reflexivity axioms. We define a binomial random model of finite 
    $\sigma$-structures that satisfy $T$ and show that first order properties have 
    well defined asymptotic probabilities when the expected number of tuples satisfying
    each relation in $\sigma$ is linear.
    It is also shown that those limit probabilities are well-behaved with
    respect to some parameters that represent the density of tuples satisfying $R$
    for each relation $R$ in the vocabulary $\sigma$. 
    An application of these results to the problem of random Boolean 
    satisfiability is presented afterwards. 
    We show that in a random $k$-CNF formula over $n$ variables where
    each possible clause occurs with probability $\sim c/n^{k-1}$ independently any 
    first order property of $k$-CNF formulas that
    implies unsatisfiability does almost surely not hold as $n$ tends to infinity.

@@

The short proof of this theorem is as follows: 
It is a known fact that there are positive constants
$c_0\leq c_1$ such that $G(n, c/n)$ is a.a.s $3$-colorable
if $c<c_0$ and it is a.a.s non $3$-colorable if $c>c_1$ 
REFERENCES NEEDED.
Suppose $P$ is a FO graph property that implies
non-$3$-colorability. Then, because of this implication,
for all values of $c$
\[\Ln \mathrm{Pr}\big( G(n, c/n) 
\text{ satisfies } P \big) \leq \Ln \mathrm{Pr}\big( G(n, c/n) 
\text{ is not }	3\text{-colorable}\big).\]
In consequence the asymptotic probability that $G(n,c/n)$ 
satisfies $P$ is zero when $c<c_0$. By Lynch's theorem, if 
$P$ is definable in FO logic then this asymptotic probability
varies analytically with $c$. Using the fact that any analytic 
function that takes value zero in a non-empty interval must 
equal zero everywhere, we obtain that $G(n,c/n)$ a.a.s does 
not satisfy $P$ for any value of $c$. 
As a consequence the theorem follows.  \par

@@

Given a positive natural number $n$, we will write
$[n]$ to denote the set ${1,2,\dots,n}$.\par
Given a set $S$ and a natural number $k\in \N$
we will use $\binom{S}{k}$ to denote the set of 
subsets of $S$ whose size is $k$. \par
Given numbers, $n,m\in \N$ with $m\leq n$ we denote by
$(n)_m$ the $m$-th falling factorial of $n$. \par
We will use the convention that over-lined variables
, like $\overline{x}$, denote ordered tuples of arbitrary length.
Given an ordered tuple $\overline{x}$
we define the number $len(\overline{x})$ as its length. 
Given a tuple $\overline{x}$ and an element $x$ the expression
$x\in \overline{x}$ means that $x$ appears as some coordinate
in $\overline{x}$. 
Given a map $f:X\rightarrow Y$ between two sets $X, Y$ and 
an ordered tuple $\overline{x}:=(x_1,\dots,x_a)\in X^*$ 
we define $f(\overline{x})\in Y^*$ as the tuple 
$(f(x_1),\dots,f(x_a))$.
Given two tuples $\overline{x},\overline{y}$
we write $\overline{x}^\smallfrown \overline{y}$ to denote their 
concatenation.
\par

Given a set
$S$ and a number $n\in \N$ with $n\leq |S|$ we define
$(S)_n$ as the subset of $S^n$ consisting of the $n$-tuples
whose coordinates are all different. 
We also define $S^*:=\bigcup_{n=0}^\infty S^n$ and
$(S)_*:=\bigcup_{n\leq |S|} (S)_n$. \par

Let $S$ be a set, $a$ a positive natural number, 
and $\Phi$ a group of permutations over 
$[a]$. Then $\Phi$ acts naturally over
$S^a$ in the following way: Given $g\in \Phi$ and
$\overline{x}:=(x_1,\dots,x_a)\in S^a$ we define 
$g\cdot \overline{x}$ 
as the tuple $(x_{g(1)},\dots,x_{g(a)})$. 
We will denote by $S^a/\Phi$ to the quotient
of the set $S^a$ by this action. Given an element
$\overline{x}:=(x_1,\dots, x_a)\in S^a$ we will denote its equivalence
class in $S^a/\Phi$ by $[x_1,\dots,x_a]$ or $[\overline{x}]$.
Thus, for any
$g\in \Phi$, by definition $[x_1,\dots,x_a]=[x_{g(1)}
,\dots,x_{g(a)}]$. \par
The notations $\overline{x}$ and
$(x_1,\dots, x_a)$ 
will be reserved 
to ordered tuples while 
$[\overline{x}]$ and
$[x_1,\dots,x_a]$ will denote ordered tuples modulo the
action of some arbitrary group of permutations. Which group is
this will depend on the ambient set where $[x_1,\dots,x_a]$ belongs
and it should either be clear from context or not be relevant.\par

@@

Structures in $\mathcal{C}$ generalize the usual notion of hypergraph
in the sense that they contain multiple ``adjacency'' relations with arbitrary 
symmetry and anti-reflexivity axioms. \par
We will use the usual graph theory nomenclature and notation with some minor changes. 
In the scope of this article we will call \textbf{hypergraphs}
to structures in $\mathcal{C}$.
Given an hypergraph $G$ we will call its \textbf{vertex set}, denoted by $V(G)$,
to its universe.\par
In order to define the edge sets of $G$ we need the following auxiliary definition
\begin{definition} 
	Let $V$ be a set, and let $R\in \sigma$.
	We define the \textbf{set of possible edges over $V$
	given by $R$} as
	\[ E_R[V]= (V^{ar(R)}/\Phi_R) \quad \setminus 
	\quad X, \]
	where
	\[
	X=
	\Big\{ [v_1,\dots,v_{ar(R)}]  
	\quad \Big| \quad
	v_1,\dots,v_{ar(R)}\in V, \,
	\text{ and } 
	 \, v_i=v_j \text{ for some } 
	\{i,j\}\in P_R \Big\}.
	\]
	We will call \textbf{edges} to the elements of
	$E_R[V]$ and we will say that the \textbf{sort} of any edge $e\in E_R[V]$
	is $R$.	In the case where $V=[n]$ we will write simply $E_R[n]$ instead
	of $E_R[[n]]$
\end{definition}

That is, $E_R[V]$ contains all the ``$ar(R)$-tuples of elements
in $V$ modulo the permutations
in $\phi_R$" 
excluding those that contain some repetition of elements in
the positions given by $P_R$.\par
Let $G$ be an hypergraph whose set of vertices is $V$ and let $R\in \sigma$
be a relation. 
We define the \textbf{edge set of $G$ given by $R$}, denoted by $E_R(G)$, 
as the set of edges $[\overline{v}]\in E_R[V]$ such that $\overline{v}\in R^G$. 
We define \textbf{the total edge set of $G$} as the set $E(G):=\cup_{R\in \sigma} E_R(G)$.
Given an edge, $e\in E(G)$ we will denote by $V(e)$
the set of all vertices that participate in $e$. 
\par
Clearly an hypergraph $G$ is completely given by its vertex set $V(G)$ and its edge 
set $ E(G)$. Notice that edges $e\in E(G)$ are sorted according to the relation they represent.
\par

@@

We define the \textbf{excess} $ex(G)$ of an hypergraph $G$ as the number
\[
ex(G):= \big(\sum_{R\in \sigma} (ar(R)-1)|E_R(G)|\big) - |V(G)|.  
\] 
That is, the excess of $G$ is its "weighted number of edges"
minus its number of vertices. \par
An hypergraph $G$ is \textbf{connected} if for any two vertices $v,u\in V(G)$
there is a sequence of edges $e_1,\dots, e_m\in E(G)$ such that
$v\in V(e_1), u\in V(e_m)$ and for each $i\in [m-1]$, 
$V(e_i)\cap V(e_{i+1})\neq \emptyset$. It holds that
$ex(G)\geq -1$ for any connected hypergraph.
\par
A connected hypergraph $G$ is a path between two of its 
vertices $v,u\in V(G)$ if $G$ 
does not contain any connected proper sub-hypergraph containing both $v,u$.
\par
A connected hypergraph $G$ is a \textbf{tree} if $ex(G)=-1$ and \textbf{dense} if $ex(G)>0$.
A connected hypergraph $G$ with $ex(G)\geq 0$ is called \textbf{saturated} 
if for any non-empty proper sub-hypergraph
$H\subset G$ it holds $ex(H)<ex(G)$. 
A connected hypergraph $G$ with $ex(G)=0$ is called \textbf{unicycle}. 
A saturated unicycle is called a \textbf{cycle}. \par
Given an hypergraph $G$ we define the following metric, $d$, over $V(G)$:
\[ d^G(u,v)= \min_{\substack{H \subset G\\ 
		H \text{ connected }\\
		u,v\in V(H)}} |E(H)| .\]
That is, the \textbf{distance} between $v$ and $u$ is the minimum number of
edges necessary to connect $v$ and $u$. 
If such number does not exist we define $d^G(u,v)=\infty$. 
When $G$ 
is understood or not relevant we will usually simply denote the 
distance by $d$ instead of $d^G$. Equivalently, the distance $d$
coincides with the usual one defined over the Gaifman graph of the structure 
$G$. The \textbf{diameter} of an hypergraph is the maximum distance between any 
two of its vertices. 
We extend naturally the distance $d$ to sets and tuples of
vertices, as usual. Given a vertex/set/tuple $X$ and a number
$r\in \N$ we define the \textbf{neighborhood}
$N^G(X;r)$, or simply $N(X;r)$ when $G$ is not relevant,
as the set of vertices $v$ such that $d^G(X,v)\leq r$.
\par

\textbf{Isomorphisms} between hypergraphs are defined the same as 
isomorphisms between relational structures. We denote the isomorphism relation
between hypergraphs by $\simeq$. 
Given and hypergraph $H$, an \textbf{automorphism} of $H$
is an isomorphism from $H$ to itself. We will denote by
$\aut(H)$ the number of such automorphisms. \par

Let $H$ be an hypergraph and let $V$ be a set. We define the
set of \textbf{copies of $H$ over $V$}, denoted as $Copies(H,V)$, 
as the set of hypergraphs 
$H^\prime$ such that
$V(H^\prime)\subset V$ and $H\simeq H^\prime$.   \par

In our proofs it will be useful to consider colorings over 
hypergraphs as a way to decorate their 
vertices with extra information. 
Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
is a pair $(H, \chi)$ where $H$ is an hypergraph
and $\chi: V(H)\rightarrow \Sigma$ is a map 
called \textbf{$\Sigma$-coloring} of $H$. \par
\textbf{Isomorphisms} between $\Sigma$-hypergraphs are just isomorphisms between the underlying
hypergraphs that also preserve their colorings. We also denote the isomorphism relation between 
$\Sigma$-hypergraphs by $\simeq$.
Given a $\Sigma$-hypergraph $(H,\chi)$,  an 
\textbf{automorphism} of $(H,\chi)$ is an 
isomorphism from it into itself, as before. We will denote
by $\aut(H,\chi)$ the number of such automorphisms. 
\par

Let $(H,\chi)$ be a $\Sigma$-hypergraph and let $V$ be a set.
As before, we define the set $Copies\big(
(H,\chi),\, \, V\big)$ as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)$ satisfying $V(H^\prime)\subset V$ and
$(H,\chi)\simeq (H^\prime,\chi^\prime)$. Let $\mathbb{H}$ be 
an isomorphism class of $\Sigma$-hypergraphs. Then the set
$Copies(\mathbb{H}, V)$ is defined as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)$ such that 
$V(H^\prime)\subset V$ and
$(H^\prime,\chi^\prime)\in \mathbb{H}$. 
Let $v\in V$ and $s\in \Sigma$. We define the
set $Copies\big(\mathbb{H}, V;\,\, (v,s)\big)$ 
as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)\in Copies(\mathbb{H}, V)$
that satisfy $v\in V(H^\prime)$ as well as
$\chi^\prime(v)=s$. \par

Given $\mathbb{H}$ an isomorphism class of hypergraphs or $\Sigma$-hypergraphs
, we define expressions
such as $ex(\mathbb{H})$, $\aut(\mathbb{H})$,
$|V(\mathbb{H})|$, $|E(\mathbb{H})|$ or
$Copies(\mathbb{H},V)$ via representatives of $\mathbb{H}$.\par

@@

%Let $G_n$ denote a random hypergraph in 
%$G^\mathcal{C}(n,\overline{p})$, where 
%$\bar{p}:=p_1,\dots,p_t$, and 
%we allow each $p_i$ to depend on $n$. 
As in the case of Lynch's theorem, we are interested in the
"sparse regime" of $G^\mathcal{C}(n,\overline{p})$, were the 
expected number of edges each sort is linear. 
%In other words, we want that
%$\mathrm{E}[m_i(G_n)]=\Theta(n)$ for all $i$'s.
This is achieved when each of the $p_R$'s are 
of the form $\beta_R/n^{ar(R)-1}$ for some 
positive real numbers $\InR{\beta}$.
We will denote a random sample of 
$G^\mathcal{C}\left(n,\left\{p_R\right\}_{R\in\sigma}\right)$
by $G_n\left(\InR{\beta}\right)$ when the probabilities $p_R$
satisfy $p_R(n)\sim \beta_R/n^{ar(R)-1}$ for all $R\in \sigma$.
When the choice of $\InR{\beta}$ is not relevant
we will write $G_n$ instead of 
$G_n\left(\InR{\beta}\right)$.\par

@@

We assume familiarity with Ehrenfeucht-Fraisse (EF) games.
An introduction to the subject can be found in
\cite[Section 2]{finitemodeltheory1}, for example. Given
hypergraphs $H_1$ and $H_2$ we denote the $k$-round EF game played 
on $H_1$ and
$H_2$ by $\ehr_k(H_1;H_2)$.
The following is satisfied:
